---
title: "pclm vignette"
author: "Marius Pascariu and Silvia Rizzi"
date: "May 6, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

So far the package has 3 elements: the pclm function, a generic plot function and HMD data ($hmddx$) for testing purposes. See below how it works.

## 1. How to install the packages from Github

1. Make sure you have the most recent version of R
2. Run the following code in your R console 

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("mpascariu/pclm")
```


## 2. Estimation of smooth age at death distributions from grouped death counts

### Data

```{r}
library(pclm)

# Select data
year    = 2014
sex     = "Total"

deaths <- hmdDx[hmdDx$Year == year, ]

# Aggregate them artificially in 5-years age classes with 85+ 
# add last bin with 0 counts to complete the histogram
breaks = c(seq(0,85,5),115,130)
deaths$Groups_Counts <- c(rep(1:17, each = 5), rep(18, 26))
aggredate_dx <- aggregate(deaths$Total, FUN = "sum",
                 by = list(deaths$Groups_Counts))$x
aggredate_dx <-  c(aggredate_dx, 0)
```

### Fit model
```{r}
# Fit model
mod = pclm(dta = aggredate_dx, breaks, ci.level = 0.05)

mod
```

The function generates different types of output stored in the $mod$ object:
```{r}
ls(mod)
```

Fitted values together with 95% confidence intervals:
```{r}
head(fitted.values(mod))
```


### Generic plot
```{r}
# Generic plot
plot(mod)
# Add real data on top
lines(0:110, deaths$Total, type = "o", col = "black") 
```

